---
title: "Statistics Quiz - Quarto Generated Figures"
format: html
---

# Pool: Statistics with R-Generated Plots

This quiz demonstrates how to use dynamically generated figures from R code chunks in your exam questions.

# Section: Descriptive Statistics

## 1. Histogram Interpretation [2 pts]

```{r}
#| echo: false
#| fig-width: 5
#| fig-height: 3.5
#| label: fig-histogram

set.seed(42)
data <- rnorm(500, mean = 100, sd = 15)
hist(data, 
     main = "Distribution of Test Scores",
     xlab = "Score", 
     ylab = "Frequency",
     col = "steelblue",
     border = "white",
     breaks = 20)
abline(v = mean(data), col = "red", lwd = 2, lty = 2)
```

Based on the histogram above, which statement is most accurate?

a) The distribution is right-skewed
b) **The distribution is approximately normal** ✓
c) The distribution is left-skewed
d) The distribution is bimodal

## 2. [TF] The red dashed line represents the median. → False

# Section: Regression Analysis

## 3. Scatter Plot Correlation [3 pts]

```{r}
#| echo: false
#| fig-width: 5
#| fig-height: 4
#| label: fig-scatter

set.seed(123)
x <- seq(1, 50, length.out = 40)
y <- 2 * x + 10 + rnorm(40, sd = 8)

plot(x, y, 
     pch = 19, 
     col = "darkblue",
     main = "Study Hours vs Exam Score",
     xlab = "Study Hours",
     ylab = "Exam Score")
abline(lm(y ~ x), col = "red", lwd = 2)
```

What type of relationship does this scatter plot show?

*a) Strong positive linear relationship
b) Weak positive linear relationship
c) Strong negative linear relationship
d) No relationship

## 4. Based on the regression line, approximately what score would you predict for 30 study hours? [2 pts]

```{r}
#| echo: false
#| fig-width: 5
#| fig-height: 4
set.seed(123)
x <- seq(1, 50, length.out = 40)
y <- 2 * x + 10 + rnorm(40, sd = 8)
plot(x, y, pch = 19, col = "darkblue",
     main = "Study Hours vs Exam Score",
     xlab = "Study Hours", ylab = "Exam Score")
abline(lm(y ~ x), col = "red", lwd = 2)
abline(v = 30, col = "gray", lty = 3)
abline(h = 70, col = "gray", lty = 3)
points(30, 70, pch = 4, col = "red", cex = 2, lwd = 2)
```

a) 50
b) 60
c) **70** ✓
d) 80

# Section: Probability Distributions

## 5. Normal Distribution [2 pts]

```{r}
#| echo: false
#| fig-width: 6
#| fig-height: 4
#| label: fig-normal

x <- seq(-4, 4, length.out = 200)
y <- dnorm(x)

plot(x, y, type = "l", lwd = 2, col = "darkblue",
     main = "Standard Normal Distribution",
     xlab = "Z-score", ylab = "Density")

# Shade area between -1 and 1
x_shade <- c(-1, seq(-1, 1, length.out = 100), 1)
y_shade <- c(0, dnorm(seq(-1, 1, length.out = 100)), 0)
polygon(x_shade, y_shade, col = rgb(0.2, 0.4, 0.8, 0.3), border = NA)

# Add labels
text(0, 0.15, "≈68%", cex = 1.2, font = 2)
abline(v = c(-1, 1), col = "red", lty = 2)
```

The shaded region in the graph represents approximately what percentage of the data in a normal distribution?

a) 50%
b) **68%** ✓
c) 95%
d) 99%

## 6. [Essay, 10pts] Interpretation

Looking at the normal distribution above, explain the empirical rule (68-95-99.7 rule) and describe how it applies to real-world data.
